\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-08-25 analysis/paper/paper.Rmd
added smoothCoxComment,recolor,missingFigurelabel

Our first comparison plot examines the covariates that were selected between all three hazard functions. Note that Cox regression without penalization selected more covariates than the other two, but only the intersection of coefficients with values greater than 0 are displayed in \ref{fig:cs3lolliPlot}. A visible tendency is for Cox regression to have larger estimated coefficients. This is expected, as there are no restrictions on the size of coefficients. The smallest coefficient estimates are found in penalized logistic model, aside from cancer state (cano).

@@

>>>>

@@

Our first comparison plot examines the covariates that were selected between all three hazard functions. Note that Cox regression without penalization selected more covariates than the other two, but only the intersection of coefficients with values greater than 0 are displayed in Figure \ref{fig:cs3lolliPlot}. A visible tendency is for Cox regression to have larger estimated coefficients. This is expected, as there are no restrictions on the size of coefficients. The smallest coefficient estimates are found in penalized logistic model, aside from cancer state (cano).

### 2020-08-25 analysis/paper/paper.tex
added smoothCoxComment,recolor,missingFigurelabel

This report was generated on 2020-08-25 12:59:22 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
#> LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.6             glue_1.4.1               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.1              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.1               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.06.25 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.0.1     fs_1.4.2           
#>  [7] base64enc_0.1-3     rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.0      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.61       tools_4.0.2         gtable_0.3.0       
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        conquer_1.0.1       iterators_1.0.12   
#> [37] xfun_0.16           rvest_0.3.6         lifecycle_0.2.0    
#> [40] polspline_1.1.19    muhaz_1.2.6.1       MASS_7.3-51.6      
#> [43] zoo_1.8-8           hms_0.5.3           sandwich_2.5-1     
#> [46] SparseM_1.78        RColorBrewer_1.1-2  rticles_0.14       
#> [49] yaml_2.2.1          gridExtra_2.3       rms_6.0-1          
#> [52] rpart_4.1-15        latticeExtra_0.6-29 stringi_1.4.6      
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.7         
#> [58] shape_1.4.4         mets_1.2.7.1        rlang_0.4.7        
#> [61] pkgconfig_2.0.3     matrixStats_0.56.0  evaluate_0.14      
#> [64] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [67] cmprsk_2.2-10       tidyselect_1.1.0    deSolve_1.28       
#> [70] R6_2.4.1            generics_0.0.2      Hmisc_4.4-0        
#> [73] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [76] pillar_1.4.6        haven_2.3.1         foreign_0.8-80     
#> [79] mgcv_1.8-31         nnet_7.3-14         mstate_0.2.12      
#> [82] modelr_0.1.8        crayon_1.3.4        rmarkdown_2.3      
#> [85] jpeg_0.1-8.1        grid_4.0.2          readxl_1.3.1       
#> [88] blob_1.2.1          reprex_0.3.0        digest_0.6.25      
#> [91] webshot_0.5.2       numDeriv_2016.8-1.1 stats4_4.0.2       
#> [94] munsell_0.5.0       viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

>>>>

This report was generated on 2020-08-25 13:52:10 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
#> LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] scales_1.1.1              forcats_0.5.0            
#>  [3] stringr_1.4.0             dplyr_1.0.1              
#>  [5] purrr_0.3.4               readr_1.3.1              
#>  [7] tidyr_1.1.1               ggplot2_3.3.2            
#>  [9] tidyverse_1.3.0           lubridate_1.7.9          
#> [11] visreg_2.7.0              tibble_3.0.3             
#> [13] riskRegression_2020.06.25 prodlim_2019.11.13       
#> [15] flexsurv_1.1.1            survival_3.2-3           
#> [17] pracma_2.2.9              magrittr_1.5             
#> [19] kableExtra_1.1.0          glmnet_4.0-2             
#> [21] Matrix_1.2-18             data.table_1.13.0        
#> [23] cowplot_1.0.0             colorspace_1.4-1         
#> [25] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] htmlTable_2.0.1     fs_1.4.2            base64enc_0.1-3    
#>  [7] rstudioapi_0.11     MatrixModels_0.4-1  fansi_0.4.1        
#> [10] mvtnorm_1.1-1       xml2_1.3.2          codetools_0.2-16   
#> [13] knitr_1.29          Formula_1.2-3       jsonlite_1.7.0     
#> [16] broom_0.7.0         cluster_2.1.0       dbplyr_1.4.4       
#> [19] png_0.1-7           compiler_4.0.2      httr_1.4.2         
#> [22] backports_1.1.8     assertthat_0.2.1    cli_2.0.2          
#> [25] acepack_1.4.1       htmltools_0.5.0     quantreg_5.61      
#> [28] tools_4.0.2         gtable_0.3.0        glue_1.4.1         
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        conquer_1.0.1       iterators_1.0.12   
#> [37] xfun_0.16           rvest_0.3.6         lifecycle_0.2.0    
#> [40] polspline_1.1.19    muhaz_1.2.6.1       MASS_7.3-51.6      
#> [43] zoo_1.8-8           hms_0.5.3           sandwich_2.5-1     
#> [46] SparseM_1.78        RColorBrewer_1.1-2  rticles_0.14       
#> [49] yaml_2.2.1          gridExtra_2.3       rms_6.0-1          
#> [52] rpart_4.1-15        latticeExtra_0.6-29 stringi_1.4.6      
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.7         
#> [58] shape_1.4.4         mets_1.2.7.1        rlang_0.4.7        
#> [61] pkgconfig_2.0.3     matrixStats_0.56.0  evaluate_0.14      
#> [64] lattice_0.20-41     htmlwidgets_1.5.1   cmprsk_2.2-10      
#> [67] tidyselect_1.1.0    deSolve_1.28        R6_2.4.1           
#> [70] generics_0.0.2      Hmisc_4.4-0         multcomp_1.4-13    
#> [73] DBI_1.1.0           withr_2.2.0         pillar_1.4.6       
#> [76] haven_2.3.1         foreign_0.8-80      mgcv_1.8-31        
#> [79] nnet_7.3-14         mstate_0.2.12       modelr_0.1.8       
#> [82] crayon_1.3.4        rmarkdown_2.3       timereg_1.9.6      
#> [85] jpeg_0.1-8.1        grid_4.0.2          readxl_1.3.1       
#> [88] blob_1.2.1          reprex_0.3.0        digest_0.6.25      
#> [91] webshot_0.5.2       numDeriv_2016.8-1.1 stats4_4.0.2       
#> [94] munsell_0.5.0       viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}
